
    \documentclass{resume}

    \name{ Shubham Kumar }

    \contact{
        \faEnvelope\ shubhamkr77555@gmail.com \quad | \quad
        \faPhone\ +91 7257912483
    }

    \begin{document}

    \begin{rSection}{Summary}
    Highly skilled Blockchain Engineer with expertise in designing, developing, testing, and maintaining distributed blockchain-based networks. Proficient in C++, Java, JavaScript, algorithms, data structures, and cryptography. Proven ability to support P2P networks and contribute to open-source codebases. Skilled in concurrency and bitcoin blockchains.
    \end{rSection}

    \begin{rSection}{Education}
    
    \textbf{ Vellore Institue of Technology } \hfill BTech. in Computer Science Engineering\\
    CGPA / Percentage: 8.8\\[6pt]
    
    \textbf{ Delhi Public School } \hfill Senior Secondary Education (CBSE)\\
    CGPA / Percentage: 93.6\\[6pt]
    
    \textbf{ Delhi Public School } \hfill High School Education (CBSE)\\
    CGPA / Percentage: 95.6\\[6pt]
    
    \end{rSection}

    \begin{rSection}{Experience}
    \textbf{Full Stack Developer Intern} at Just Logic Software Pvt. Ltd. \hfill (null -- null)\\
-- - Developed 3+ production-ready modules (React.js, Node.js, REST APIs), deployed to live users.\\
-- - Optimized MongoDB queries, reducing data retrieval time by 30\% for 10k+ records.\\
-- - Collaborated in a 6-member Agile team, delivering 5+ full-stack features within sprint deadlines.

    \end{rSection}

    \begin{rSection}{Projects}
    \textbf{Nexus}: Built a student-centric platform during a 48-hour hackathon with a team of 3, helping users reconnect lost belongings and match with peers having complementary skills. Designed and developed a responsive front-end using HTML, CSS, and vanilla JavaScript, ensuring smooth usability across devices. Collaborated with backend and design teammates to deliver an MVP, integrating authentication, UI, and APIs.
    \end{rSection}

    \begin{rSection}{Skills}
    
    Java\\
    
    \end{rSection}

    \begin{rSection}{Certifications}
    \textbf{Data Structures \& Algorithms Mastery}: Achieved LeetCode Contest Rating of 1750 (Top 9\% globally) and solved 600+ problems.\\
    \end{rSection}

    \end{document}
    